Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-07 hpmoon-asoco.tex
Some comments for reviewer #4

% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
\begin{bluecolor}
One of the methods that are most extensively used  to deal with high-dimensional, multi-objective optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}. However, only decomposable problems could strictly be implemented in parallel this way. A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism}, is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation. 
\end{bluecolor}

@@

Usually an EA starts by generating a set of random solutions, called
\emph{population}, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} value that describes how good the individual is
with regard to the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

EAs have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
One of the best known and referenced MOEAs
\citep{Dorronsoro13superlinear} is the {\em 
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, which are divided into different ranks, based on 
dominance, to be selected for the next generations.

@@

In our previous work \citep{Garcia16hpmoon} we used this method in a
preliminary experimental setup, although it is worth mentioning we are
establishing its name and acronym in this paper for the first time.
We \textcolor{blue}{show}
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, we showed that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically \textcolor{blue}{sets} the size of the overlapped
sections depending on the number of available islands, comparing it with previous versions.

@@

>>>>

% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
\begin{bluecolor}
One of the methods that are most extensively used  to deal with high-dimensional, multi-objective optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}. However, only decomposable problems could strictly be implemented in parallel this way. A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism} is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation. 
\end{bluecolor}

@@

Usually an EA starts by generating a \emph{population}, that is, a set of random solutions, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} value that describes how good the individual is
solving the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

EAs were extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
One of the best known and referenced MOEAs
\citep{Dorronsoro13superlinear} is the {\em 
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, which are divided into different ranks, based on 
dominance, to be selected for the next generations.

@@

In our previous work \citep{Garcia16hpmoon} we used this method in a
preliminary experimental setup, although it is worth mentioning we are
establishing its name and acronym in this paper for the first time.
We \textcolor{blue}{show}
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, we showed that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more extensive parameter evaluation. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically \textcolor{blue}{sets} the size of the overlapped
sections depending on the number of available islands, comparing it with previous versions.

@@

% There's no mention of the type of the benchmark problems. Insert here some characterization, including whether they are epistatic or not - JJ
